Domain-Driven Generative Data Model for BigPetStore

### 2014-07-16 bdcloud_paper/latex/paper.tex
Add initial benchmark data

\section{Example Analysis of Generated Data}
\subsection{Size, Scale}
[number of stores, number of customers, time window for simulations]

@@

>>>>

\section{Example Analysis of Generated Data}
Transaction data for 10 stores, 10,000 customers, and 4 years of simulated time totaling 100 MB was generated using the Python implementation.

@@

\section{Scaling of Data Size and Run Time}
BigPetStore aims to scale from a local desktop to a large cluster. As a result, we benchmarked the generation of data on a laptop with a 2 GHz Intel Core i7 CPU, 8 GB of RAM, and a 256 GB SSD using the Python implementation with a single thread. Using the test setup, between 1,500 and 2,000 transactions can be generated per second (Table~\ref{tab:benchmarks}).

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Benchmarks of Data Generator}
\label{tab:benchmarks}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{|p{0.75cm}||p{1.2cm}||p{1cm}||p{1.25cm}||p{1cm}||p{1cm}|}
\hline
Stores & Customers & Simulated Time (years) & Transactions & Data Size (MB) & Run Time (min)\\ \hline
10 & 10,000 & 1 & 279,870 & 18 & 3.5 \\ \hline
%10 & 100,000 & 1 & 
100 & 10,000 & 1 & 279,586 & 18 & 3.5 \\ \hline
% 100 & 100,000 & 1 & 
10 & 1,000 & 5 & 123,309 & 8 & 1.1 \\ \hline
100 & 1,000 & 5 & 127,064 & 8 & 1.2 \\ \hline
10 & 10,000 & 5 & 1,275,542 & 84 & 11.0 \\ \hline
%10 & 100,000 & 5 & 
100 & 10,000 & 5 & 1,268,403 & 84 & 10.5 \\ \hline
\end{tabular}
\end{table}

The number of transactions (and hence, data size) grows as $O(N_c T)$ where $N_c$ is the number of customers and $T$ is the amount of time to be simulated. The amount of data generated can be scaled as large as necessary simply by increasing $N_c$ and $T$. Five years of transactions for 100,000 customers will generate approximately 1 GB of data. A terabyte of data can be generated by simulating 100 million customers over five years.
